---
title: "Reproducible Research: Peer Assessment 1"
author: "Greg Lever"
date: "12 November 2014"
output: 
  html_document:
    keep_md: true
---

```{r, echo=FALSE}
### Loading and preprocessing the data
### The following reads in the CSV data and converts the date column into a Date type:
activityDF <- read.csv("./activity.csv")
activityDF$date <- as.Date(activityDF$date, format="%Y-%m-%d")
```

## What is mean total number of steps taken per day?
The following is a histogram of the total number of steps taken over each day:
```{r, echo=FALSE}
TotSteps <- aggregate(steps ~ date, data=activityDF, sum, na.action = na.omit)
hist(TotSteps$steps, xlab="Total Number of Steps", main="Total Steps Taken")
```

The mean and median total number of steps taken per day are as follows:
```{r, echo=FALSE, results="asis"}
library(knitr)
MedianSteps <- aggregate(steps ~ date, data=activityDF, median, na.action = na.omit)
MeanMedianSteps <- aggregate(steps ~ date, data=activityDF, mean, na.action = na.omit)
MeanMedianSteps$Median_Steps <- MedianSteps$steps
colnames(MeanMedianSteps) <- c("Date", "Mean_Steps", "Median_Steps")
kable(MeanMedianSteps, digits=2)
```

## What is the average daily activity pattern?

```{r, echo=FALSE}
IntervalStepsMean <- aggregate(steps ~ interval, data=activityDF, mean, na.action = na.omit)
plot(IntervalStepsMean$interval, IntervalStepsMean$steps, type="l", xlab="5-minute Interval", ylab="Average number of steps taken")
```

```{r, echo=FALSE}
maxSteps <- IntervalStepsMean[which.max(IntervalStepsMean$steps),]$steps
maxInterval <- IntervalStepsMean[which.max(IntervalStepsMean$steps),]$interval
```

On average, across all the days in the dataset the maximum average number of steps taken was `r maxSteps` and this maximum occurred at interval `r maxInterval`

## Imputing missing values

```{r, echo=FALSE}
missingValues <- sum(is.na(activityDF$steps))
```

The total number of rows with `NA`s is `r missingValues`.       

## Are there differences in activity patterns between weekdays and weekends?
